Supporting Information

### 2022-03-30 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
supporting info updated

**Figure S6** Association between the frequency and specificity of the different groups on motif positions.

**Figure S7** Frequency of floral visitor groups and number of indirect interactions per motif positions.

**Figure S8** Frequency of plant groups and number of indirect interactions per motif positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%'}

@@

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

>>>>

**Figure S6** Association between the percentile and specificity of the different plant and floral visitor groups on motif positions.

**Figure S7** Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions.

**Figure S8** Frequency of floral visitor groups and number of indirect interactions per motif positions.

**Figure S9** Frequency of plant groups and number of indirect interactions per motif positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile and specialization of the different plant and floral visitor groups on motif positions"}

@@

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity",scale="response", by="Group",line.par = list(col = 'black'),points=list(size=0),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")+ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",scale="response",points=list(size=0),
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions"}

library(visreg)
# Pollinator Model REAL OUTPUTS!!!

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Indirect_interactions", scale="response", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Number of indirect interactions") + ylab("Percentile")+
 # scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
  scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors") +ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Indirect_interactions,Percentil), alpha=0.5)

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Indirect_interactions",line.par = list(col = 'black'), by="Group",scale="response",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Number of indirect interactions") + ylab("Percentile")+
  #scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Indirect_interactions,Percentil), alpha=0.5)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
